Report

### 2015-09-04 Report Aug 5 2015/Report Aug 2015.tex
write a simple real SVR on matlab
modified matlab code for real SVR
modification of matlab and C code

\begin{figure}
\centering
\def\svgwidth{\columnwidth}
\input{epsilon-SVR.pdf_tex}
\caption{}
\label{epsilon-SVR}
\end{figure}

@@

The alternate form can be written as 
\begin{IEEEeqnarray}[\relax]{l}
\nonumber
maximize \quad \Theta^{r}=-\frac{1}{2}(\alpha-\hat{\alpha})^{T}\mathbf{K}^{r}(\alpha-\hat{\alpha})+Re(\mathbf{y})^{T}(\alpha-\hat{\alpha})-\epsilon(\mathbf{e}^{T}(\alpha+\hat{\alpha}))+C(\mathbf{e}^{T}(\tilde{R}(\xi^{r})-\tilde{R}(\hat{\xi}^{r})))\\
\left\{\begin{array}{ll}
0\leq \alpha(\hat{\alpha})\leq C\tilde{R}(\xi^{r})(\tilde{R}(\hat{\xi}^{r}))\\
\xi^{r}(\hat{\xi}^{r})\geq 0\\
\end{array}\right.
\label{complex duality real part vectorizes}
\end{IEEEeqnarray}

\begin{IEEEeqnarray}[\relax]{l}
\nonumber
maximize \quad \Theta^{i}=-\frac{1}{2}(\beta-\hat{\beta})^{T}\mathbf{K}^{r}(\beta-\hat{\beta})+Im(\mathbf{y})^{T}(\beta-\hat{\beta})-\epsilon(\mathbf{e}^{T}(\beta+\hat{\beta}))+C(\mathbf{e}^{T}(\tilde{R}(\xi^{i})-\tilde{R}(\hat{\xi}^{i})))\\
\left\{\begin{array}{ll}
0\leq \beta(\hat{\beta})\leq C\tilde{R}(\xi^{i})(\tilde{R}(\hat{\xi}^{i}))\\
\xi^{i}(\hat{\xi}^{i})\geq 0\\
\end{array}\right.
\label{complex duality imaginary part vectorized}
\end{IEEEeqnarray}
where $(\alpha-\hat{\alpha})$, $(\beta-\hat{\beta})$,$Re(\mathbf{y})$, $Im(\mathbf{y})$ denote vectors, $\mathbf{e}=[1,1,\ldots, 1]^{T}\in \mathbb{R}^{N_{r}}$, $\mathbf{K}^{r}$ denotes the matrix consist of real  part of kernel components. Observe that solving (\ref{complex duality real part vectorizes}) and (\ref{complex duality imaginary part vectorized}) are equivalent to solving two independent real Support vector regression task (dual channel), only the real part of kernel matrix is required for each channel. In section \ref{stopping criteria}, we will further show that from the statistic analyst of channel orthogonality (which is also named channel hardening phenomenon), the imaginary part of kernel matrix can also be omitted in stopping condition. Therefore, in large MIMO scenario, our CSVR-MIMO detector can save half of the cost in kernel matrix computation.    
\section{Work Set Selection and Solver}\label{WSS}
(\ref{final complex lagrange duality}) can be viewed as quadratic optimization problem, The traditional optimization algorithms such as Newton, Quasi Newton can not be directly applied to this problem, because the sparseness of kernel matrix $\mathbf{K}$ can not be guaranteed, so that a prohibitive storage may be required when dealing with large data set.

@@

Because (\ref{complex duality real part}) and (\ref{complex duality imaginary part}) are symmetric, in this section we discuss real part only. By dividing the variables into work set $S$ and fixed set $N$, we have $(\alpha, \hat{\alpha})=((\alpha_{N}, \hat{\alpha}_{N})\mathbf{e}_{N}+(\alpha_{S}+\hat{\alpha}_{S})\mathbf{e}_{S})$, where $\mathbf{e}_{K}$ denotes the modified vector of $\mathbf{e}$ with the components in set $K$ zeroed, for sake of brevity， we replace $\alpha_{K}\mathbf{e}_{K}$ by $\alpha_{K}$. Thus (\ref{complex duality real part vectorizes}) can be changed to:
\begin{IEEEeqnarray}[\relax]{l}
\nonumber
maximize\quad \Theta^{r}=-\frac{1}{2}[(\alpha-\hat{\alpha})_{S}^{T}\mathbf{K}_{SS}^{r}(\alpha-\hat{\alpha})_{S}+2(\alpha-\hat{\alpha})_{N}^{T}\mathbf{K}_{NS}^{r}(\alpha-\hat{\alpha})_{S}]
+Re(\mathbf{y})_{S}^{T}(\alpha-\hat{\alpha})_{S}-\\
\nonumber
\epsilon(\mathbf{e}^{T}(\alpha+\hat{\alpha})_{S})
-\frac{1}{2}(\alpha-\hat{\alpha})_{N}^{T}\mathbf{K}_{NN}^{r}(\alpha-\hat{\alpha})_{N}+Re(\mathbf{y})_{N}^{T}(\alpha-\hat{\alpha})_{N}-\epsilon(\mathbf{e}^{T}(\alpha+\hat{\alpha})_{N})\\+C(\mathbf{e}^{T}(\tilde{R}(\xi^{r})-\tilde{R}(\hat{\xi}^{r}))),
\label{real part decomposition}
\end{IEEEeqnarray}
Where $\mathbf{K}^{r}=\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
\mathbf{K}^{r}_{SS}& \mathbf{K}^{r}_{SN}\\
\mathbf{K}^{r}_{NS}& \mathbf{K}^{r}_{NN}
\end{IEEEeqnarraybox*}\right]$, $\mathbf{K}^{r}_{SN}=\mathbf{K}^{r}_{NS}$
and  $\alpha_{S}\in \mathbb{R}^{N_{r}}$ denotes the vector with the components that do not belong to $S$ zeroed. Therefore the sub-optimization problem is formulated as 
\begin{equation}
maximize\quad \Theta_{S}^{r}=-\frac{1}{2}[(\alpha-\hat{\alpha})_{S}^{T}\mathbf{K}_{SS}^{r}(\alpha-\hat{\alpha})_{S}]+[Re(\mathbf{y})_{S}^{T}-(\alpha-\hat{\alpha})_{N}^{T}\mathbf{K}_{NS}^{r}
](\alpha-\hat{\alpha})_{S}-\epsilon[\mathbf{e}_{S}^{T}(\alpha+\hat{\alpha})_{S}],
\label{subset optimization}
\end{equation}
In decomposition method, a proper work set selection strategy is required so that acceptable speed and performance can be guaranteed. One approach is to choose dual variable pairs that violate KKT conditions, so that after each iteration, the objective function can be increased according to Osuna's theorem\cite{inproved training algorithms for support vector machines}, Heuristic methods are used in [\cite{SMO}] in order to accelerate process, in work set selection process, the algorithm first searches among the non-bound variables (that is $0<\alpha<C\tilde{R}(\xi)$), which are more likely to violate KKT condition, then searching the whole dual variable set, the second dual variable that can maximize optimization step of the first coordinate is chosen, approximate step size is used as evaluator for sake of reducing computational cost. Lin propose another work set selection strategy based on an alternative form of KKT condition.

@@

maximize\quad \bigtriangledown \Theta_{S}=\Theta((\alpha+\delta_{S}\mathbf{e}_{S}), (\hat{\alpha}+\hat{\delta}_{S}\mathbf{e}_{S}))-\Theta(\alpha, \hat{\alpha}),

@@

In our regression model, the offset is omitted, therefore different from SMO type algorithms, there is no linear equation constraint as shown in (\ref{dual objective function1}), it is possible to update only one variable pair in each iteration. However, recent work shows more efficient work set selection strategy based on maximum gain selection approaches, that choose two pair of dual variables can reduce computational cost while maintaining the comparable performance with that with offset \cite{Training without offset}. Here we propose sequential 1-D work set selection, which can approximate the effect of optimal 2-D work set selection. There is only $O(n)$ searching times required for the former one while the later one need $O(n^{2})$ searching times.   

>>>>

\begin{figure}
\centering
\def\svgwidth{\columnwidth}
\input{epsilon-SVR.pdf_tex}
\caption{$\epsilon$-Support Vector Regression and Risk Functional}
\label{epsilon-SVR}
\end{figure}

@@

The alternate form can be written as 
\begin{IEEEeqnarray}[\relax]{l}
\nonumber
maximize \quad \Theta^{r}=-\frac{1}{2}(\alpha-\hat{\alpha})^{T}\mathbf{K}^{r}(\alpha-\hat{\alpha})+Re(\mathbf{y})^{T}(\alpha-\hat{\alpha})-\epsilon(\mathbf{e}^{T}(\alpha+\hat{\alpha}))+C(\mathbf{e}^{T}(\tilde{R}(\xi^{r})+\tilde{R}(\hat{\xi}^{r})))\\
\left\{\begin{array}{ll}
0\leq \alpha(\hat{\alpha})\leq C\tilde{R}(\xi^{r})(\tilde{R}(\hat{\xi}^{r}))\\
\xi^{r}(\hat{\xi}^{r})\geq 0\\
\end{array}\right.
\label{complex duality real part vectorizes}
\end{IEEEeqnarray}

\begin{IEEEeqnarray}[\relax]{l}
\nonumber
maximize \quad \Theta^{i}=-\frac{1}{2}(\beta-\hat{\beta})^{T}\mathbf{K}^{r}(\beta-\hat{\beta})+Im(\mathbf{y})^{T}(\beta-\hat{\beta})-\epsilon(\mathbf{e}^{T}(\beta+\hat{\beta}))+C(\mathbf{e}^{T}(\tilde{R}(\xi^{i})+\tilde{R}(\hat{\xi}^{i})))\\
\left\{\begin{array}{ll}
0\leq \beta(\hat{\beta})\leq C\tilde{R}(\xi^{i})(\tilde{R}(\hat{\xi}^{i}))\\
\xi^{i}(\hat{\xi}^{i})\geq 0\\
\end{array}\right.
\label{complex duality imaginary part vectorized}
\end{IEEEeqnarray}
where $(\alpha-\hat{\alpha})$, $(\beta-\hat{\beta})$,$Re(\mathbf{y})$, $Im(\mathbf{y})$ denote vectors, $\mathbf{e}=[1,1,\ldots, 1]^{T}\in \mathbb{R}^{N_{r}}$, $\mathbf{K}^{r}$ denotes the matrix consist of real  part of kernel components. Observe that solving (\ref{complex duality real part vectorizes}) and (\ref{complex duality imaginary part vectorized}) are equivalent to solving two independent real Support vector regression task (dual channel), only the real part of kernel matrix is required for each channel. In section \ref{stopping criteria}, we will further show that from the statistic analyst of channel orthogonality (which is also named channel hardening phenomenon), the imaginary part of kernel matrix can also be omitted in stopping condition. Therefore, in large MIMO scenario, our CSVR-MIMO detector can save half of the cost in kernel matrix computation.    
\section{Work Set Selection and Solver}\label{WSS}
(\ref{final complex lagrange duality}) can be viewed as quadratic optimization problem, The traditional optimization algorithms such as Newton, Quasi Newton can not be directly applied to this problem, because the sparseness of kernel matrix $\mathbf{K}$ can not be guaranteed, so that a prohibitive storage may be required when dealing with large data set.

@@

Because (\ref{complex duality real part}) and (\ref{complex duality imaginary part}) are symmetric, in this section we discuss real part only. By dividing the variables into work set $S$ and fixed set $N$, we have $(\alpha, \hat{\alpha})=((\alpha_{N}, \hat{\alpha}_{N})\mathbf{e}_{N}+(\alpha_{S}+\hat{\alpha}_{S})\mathbf{e}_{S})$, where $\mathbf{e}_{K}$ denotes the modified vector of $\mathbf{e}$ with the components in set $K$ zeroed, for sake of brevity， we replace $\alpha_{K}\mathbf{e}_{K}$ by $\alpha_{K}$. Thus (\ref{complex duality real part vectorizes}) can be changed to:
\begin{IEEEeqnarray}[\relax]{l}
\nonumber
maximize\quad \Theta^{r}=-\frac{1}{2}[(\alpha-\hat{\alpha})_{S}^{T}\mathbf{K}_{SS}^{r}(\alpha-\hat{\alpha})_{S}+2(\alpha-\hat{\alpha})_{N}^{T}\mathbf{K}_{NS}^{r}(\alpha-\hat{\alpha})_{S}]
+Re(\mathbf{y})_{S}^{T}(\alpha-\hat{\alpha})_{S}-\\
\nonumber
\epsilon(\mathbf{e}^{T}(\alpha+\hat{\alpha})_{S})
-\frac{1}{2}(\alpha-\hat{\alpha})_{N}^{T}\mathbf{K}_{NN}^{r}(\alpha-\hat{\alpha})_{N}+Re(\mathbf{y})_{N}^{T}(\alpha-\hat{\alpha})_{N}-\epsilon(\mathbf{e}^{T}(\alpha+\hat{\alpha})_{N})\\+C(\mathbf{e}^{T}(\tilde{R}(\xi^{r})+\tilde{R}(\hat{\xi}^{r}))),
\label{real part decomposition}
\end{IEEEeqnarray}
Where $\mathbf{K}^{r}=\left[\begin{IEEEeqnarraybox*}[\mysmallarraydecl][c]{,c/c,}
\mathbf{K}^{r}_{SS}& \mathbf{K}^{r}_{SN}\\
\mathbf{K}^{r}_{NS}& \mathbf{K}^{r}_{NN}
\end{IEEEeqnarraybox*}\right]$ is a permutation of $\mathbf{K}^{r}$, $\mathbf{K}^{r}_{SN}=\mathbf{K}^{r}_{NS}$ 
and  $\alpha_{S}\in \mathbb{R}^{N_{r}}$ denotes the vector with the components that do not belong to $S$ zeroed. In each iteration, in (\ref{real part decomposition}), $\alpha_{N}$ is fixed and only the sub problem that correlated to $\alpha_{S}$ is solved i.e 
\begin{equation}
maximize\quad \Theta_{S}^{r}=-\frac{1}{2}[(\alpha-\hat{\alpha})_{S}^{T}\mathbf{K}_{SS}^{r}(\alpha-\hat{\alpha})_{S}]+[Re(\mathbf{y})_{S}^{T}-(\alpha-\hat{\alpha})_{N}^{T}\mathbf{K}_{NS}^{r}
](\alpha-\hat{\alpha})_{S}-\epsilon[\mathbf{e}_{S}^{T}(\alpha+\hat{\alpha})_{S}],
\label{subset optimization}
\end{equation}
In decomposition method, a proper work set selection strategy is required so that acceptable speed and performance can be guaranteed. One approach is to choose dual variable pairs that violate KKT conditions, so that after each iteration, the objective function can be increased according to Osuna's theorem\cite{inproved training algorithms for support vector machines}, Heuristic methods are used in [\cite{SMO}] in order to accelerate process, in work set selection process, the algorithm first searches among the non-bound variables (that is $0<\alpha<C\tilde{R}(\xi)$), which are more likely to violate KKT condition, then searching the whole dual variable set, the second dual variable that can maximize optimization step of the first coordinate is chosen, approximate step size is used as evaluator for sake of reducing computational cost. Lin propose another work set selection strategy based on an alternative form of KKT condition.

@@

maximize\quad \bigtriangledown \Theta_{S}=\Theta_{S}((\alpha_{S}+\delta_{S}\mathbf{e}_{S}), (\hat{\alpha}_{s}+\hat{\delta}_{S}\mathbf{e}_{S}))-\Theta_{S}(\alpha_{S}, \hat{\alpha}_{S}),

@@

The offset term is omitted in Large MIMO system, therefore different from SMO type algorithms, there is no linear equation constraint as shown in (\ref{dual objective function1}), it is possible to update only one variable pair in each iteration. However, recent work shows more efficient work set selection strategy based on maximum gain selection approaches, that choose two pair of dual variables can reduce computational cost while maintaining the comparable performance with that with offset \cite{Training without offset}. Here we propose sequential 1-D work set selection strategy, which can approximate the performance of optimal 2-D work set selection, while only $O(n)$ searching times required for the former one instead of $O(n^{2})$ searching times.   
